|

### 2021-12-16 text/ManuscriptDraft.Rmd
Note about visualization
Minor update
Manuscript update

```{r eval = FALSE, echo=FALSE}
library(knitr)
knit('ManuscriptDraft.Rmd')
rmarkdown::render("ManuscriptDraft.Rmd", output_file = "ManuscriptDraft.docx")
system2("open","ManuscriptDraft.docx")
```

\pagebreak

@@

* **Our solution**
  + Here we demonstrate a framework for automatic flower tracking and evualutation of tracking performance
  + Ground truth tracks

@@

Monitoring of flower phenology at high temporal resolution is laboursome and time-consuming, particularly in logistically challenging environment such as the Arctic. Consequently, simple variables are often used to represent the flowering phenology of a population, such as the date for onset of flowering, often derived from weekly observations of sample plots.

Automatic image-based monitoring of flowering phenology can return phenology data for specific species at very high temporal resolution (Mann et al., in prep).

For example, phenological responses at the individual level may be indiscernible regardless of the temporal resolution of the data at population level. For example, a shortening of flower longevity may not be directly obvious at the population level. Further, investigating the association between reproductive success and timing of flowering and flower longevity requires phenology data at the level of individuals.

Does flower visitation rates and/or reproductive success depend on the timing of flowering for the individual flower?

@@

@@

The tracking algorithm has a set of user adjusted parameters that can optimise tracking accuracy.

The parameters are particularly relevant for optimal tracking of objects that are constrained to a specific area such as flowers.

It is important to note, however, that the tracking algorithm can be used to track any objects.

The tracking algorithm can be applied both offline (on a set of detections/annotations that have already been produced) or online (real-time tracking frame per frame).

The speed of the tracking algorithm depends on the computational power available as well as the number of objects that are being tracked.

![](../figures/figure_1.png){ width=100% }

**Figure 1:** Simple centroid tracking may produce erronous associations when objects move between frames. Blue shows detections in the current frame (bounding box and centroid point). Red shows centroid points for the detections in the previous frame.

@@

@@

![](../figures/figure_22.jpg){ width=100% }

@@

![](../figures/figure_3.png){ width=100% }

@@

@@

Mota counts tracking mismatches (shifts in a track).

To derive flowering length, in theory we just need to track the most extreme points correctly and don't care about other points (although we filter by length when overlap).

To associate other information to the flower, for example flower visits, we want as much as possible of the track to be correct.

Lastly, we may be interested in the number of flowers that existed in a plot. Therefore, a final way of evaluating automatic flower tracking performance is to compare the number of tracks identified by the automatic tracking with the true number of flowers in a series. These should ideally be equal.

@@

@@

## Flower phenology

@@

The code that supports the results in this paper will be made openly available at https://github.com/TECOLOGYxyz/FlowerTracking. Raw data as well as the trained flower detection model will be archived on https://zenodo.org/.

>>>>

```{r eval = FALSE, echo=FALSE}
library(knitr)
knit('ManuscriptDraft.Rmd')
rmarkdown::render("ManuscriptDraft.Rmd", output_file = "ManuscriptDraft.docx")
system2("open","ManuscriptDraft.docx")
```
\newpage

@@

* **Our solution**
  + Here we demonstrate a framework for automatic flower tracking and evaluation of tracking performance
  + Ground truth tracks

@@

Monitoring of flower phenology at high temporal resolution is laboursome and time-consuming, particularly in logistically challenging environment such as the Arctic. Consequently, simple variables are often used as proxies for the flowering phenology of a population, such as the date for onset of flowering, often derived from weekly observations of sample plots. Such proxies may fail to reveal dynamics in flowering phenology for example caused by changes in climate.

Automatic image-based monitoring of flowering phenology can return phenology data for specific species at very high temporal resolution (Mann et al., in prep), but phenological responses at the individual level may be indiscernible regardless of the temporal resolution of the data at population level. For example, a shortening of individual flower longevity may not be directly obvious at the population level. Many research questions can only be explored on the basis of individual phenology data. For example, investigating the association between reproductive success and timing of flowering and flower longevity requires phenology data at the level of individuals. Similarly, such data is necessary for investigating whether flower visitation rates and/or reproductive success depends on the timing of flowering for the individual flower.

Here, we show that information on phenology at the level of individuals can be derived from image-based monitoring of flower phenology. Further, we present and evaluate an automatic flower tracking algorithm.

@@

The annotation process is described in Mann et al., in prep, but in short: We manually annotated all flowers in the sampled image series using the rectangular bounding box tool in the VIA VGG annotation software. Further, we assigned each individual a unique ID. These annotations constitue our ground truth tracks.

@@

# 
![](../figures/figure_1.png){ width=100% }

**Figure 1:** Simple centroid tracking may produce erroneous associations when objects move between frames. Blue shows detections in the current frame (bounding box and centroid point). Red shows centroid points for the detections in the previous frame.

# 
![](../figures/figure_22.jpg){width=100%}

**Figure 2:** Simple centroid tracking may produce erroneous associations when objects move between frames. Basing the association on the running mean of the positions of the previous n number of tracks may alleviate this issue. In this case basing the association on only the previous point would produce a wrong results while basing it on the running mean would produce a correct result. Red points: Centroids for bounding boxes in current frame, blue points: Centroids for bounding boxes in previous frame; grey points: Centroids for bounding boxes in a number of frames before t-1; green points: Running mean of the previous n points. Circles delimit the two individuals.

# 
![](../figures/figure_3.png){ width=100% }

**Figure 3:** Simple centroid tracking may produce erroneous associations when objects disappear periodically from the frame. Here the top flower moves out of frame and the bottom flower would be assigned to the track of the top flower in frame t-1.

@@

The tracking algorithm has a set of user adjusted parameters that can optimize tracking accuracy. The parameters are particularly relevant for optimal tracking of objects that are constrained to a specific area such as flowers. It is important to note, however, that the tracking algorithm can be used to track any objects. The tracking algorithm can be applied both offline (on a set of detections/annotations that have already been produced) or online (real-time tracking frame per frame). The speed of the tracking algorithm depends on the computational power available as well as the number of objects that are being tracked.

@@

@@

@@

### Identifying optimal user parameters

To explore the effect of the user parameters and to identify the optimal combination of parameters for our case of tracking flowers, we followed a step wise approach. First, we ran the tracking algorithm on each of the four image series with every combination of the following settings (3.179 combinations):

max_disappeared = [0,10,20,30,40,50,60,70,80,90,100,110,120,130,140,150,160]

running_mean_threshold = [0,10,20,30,40,50,60,70,80,90,100,110,120,130,140,150,160]

max_distance = [0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000]

Note that max_distance set to zero. We identified the setting(s) that returned the lowest number of track mismatches and performed a second run with finer scaled settings for each series. Finally, we compare the tracking results between optimal settings and all parameters set to zero.

@@

The optimal way of quantifying tracking performance depends on the goal of the tracking. To associate other information obtained in the images to the individual flower, for example flower visits, we want as much as possible of the track to be correct. To derive flowering length in theory we just need to track the most extreme points correctly and don't care about the intermediate points. Lastly, we may be interested in the number of flowers that existed in a plot, in which case we want the number of tracks obtained by automatic tracking to be as close as possible to the actual number of individuals in the series.

The multiple object tracking accuracy (MOTA) score quantifies tracking performance based on counts of tracking mismatches [@bernardin2008]. Mismatches occur when objects swap track identity because they are in close vicinity to each other or when an object periodically disappears and is assigned a new track identity when it reappears. Only the shifts in tracking identity are counted as mismatches while the number of points assigned to each track is not considered.

For each series, we calculate the ratio of flowers for which the automatic tracking algorithm returns the correct flowering length compared to the ground truth tracks.

Finally, we compare the number of tracks identified by the automatic tracking with the true number of flowers in a series. These should ideally be equal.

@@

One way to plot?: Time on x-axis, gt id on y axis, tr id as colour. This will show mismatches.

@@

All three parameters make a difference.

In cases where we are tracking perfectly with maxDisap = 0, setting it any value will not make a difference. Not quite right. Explore more...

@@

The code that supports the results in this paper will be made openly available at https://github.com/TECOLOGYxyz/FlowerTracking. A publicly available web application can be accessed from the Github repository through which users can run the tracking algorithm on their own data. Raw data as well as the trained flower detection model will be archived on https://zenodo.org/.
